---
title: "Case Study"
author: "Derek Lamb"
date: "`r Sys.Date()`"
output: html_document
---
```{r packages & preferences, message = FALSE}
library(tidyverse)
library(knitr)
library(ggridges)
library(leaflet)

opts_chunk$set(
  fig.width = 6,
  out.width = "90%"
)

## These are options that i'm going to treat as default for now
## I don't love viridis, but don't have a better option yet
theme_set(theme_bw() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Get data
```{r data}
library(p8105.datasets)
data(nyc_airbnb)

df_airbnb <- nyc_airbnb |> 
  rename(borough = neighbourhood_group) |> 
  mutate(stars = review_scores_location/2)
```

## Brainstorm questions
- Where are AirBNBs expensive?
  - Borough? Neighbourhood?
- How long are AirBNBs active?
  - Are AirBNBs illegal and do they get shut down?
- Which units have the most availability?  
- How is rating impacted by location? Price?
- How many apts are run by on host?
  - Does that affect price?
  - Does that vary by neighbrhood?
- Where are AirBNBs?
  - Borough? Neighborhood?
  -Lat and long?

```{r}
df_airbnb |> 
  drop_na(stars) |> 
  ggplot(aes(x = neighbourhood, y = stars)) +
  geom_jitter() +
  facet_grid(borough ~ .)
```

```{r}
df_airbnb |> 
  drop_na(stars) |> 
  group_by(neighbourhood) |> 
  summarize(med_rating = median(stars)) |> 
  arrange(med_rating) |> 
  head()

df_airbnb |> 
  drop_na(stars) |> 
  group_by(neighbourhood) |> 
  summarize(med_rating = median(stars)) |> 
  arrange(med_rating) |> 
  tail()

```

Edgemere has the lowest median rating, 3.5 stars. This is followed by Hunts Point, Morrisania, and Port Richmond, which all have a median rating of 3.75 stars.

```{r avg borough}
df_airbnb |> 
  drop_na(stars) |> 
  group_by(borough) |> 
  summarize(mean_rating = mean(stars)) |> 
  arrange(mean_rating)
```

Manhattan has the highest average rating with a mean rating of 4.79 stars, while the Bronx has the lowest average rating of 4.44 stars.

```{r number stays per borough}
df_airbnb |> 
  drop_na(stars) |> 
  group_by(borough) |> 
  summarize(n_stays = n()) |> 
  arrange(n_stays)
```

Staten Island has the fewest airbnb stays with only 186, while Manhattan has the most at 14,541. ** Dropped NA*


## Do some EDA

```{r}
df_airbnb |> 
  count(borough)
```

```{r mean price borough}
df_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(median_price = median(price)) |> 
  pivot_wider(
      names_from = room_type,
      values_from = median_price
  )
```

```{r}
df_airbnb |> 
  filter(price < 1000, room_type == "Entire home/apt") |> 
  ggplot(aes(x = price)) +
  geom_histogram() + 
  facet_grid(.~borough)
```


```{r}
df_airbnb |> 
  filter(price >= 9500) |> 
  view()
```

```{r manhattan apts}
df_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  group_by(neighbourhood) |> 
  summarize(
    n_apt = n(),
    mean_price = mean(price)) |> 
  arrange((mean_price))
```

```{r}
df_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = price, y = neighbourhood, fill = neighbourhood)) +
  geom_density_ridges() + 
  labs(
    title = "Manhattan AirBNB price by neighborhood",
    x = "Price ($)",
    y = "Neighborhood"
  ) +
  theme(legend.position = "none")

ggsave("manhattan_airbnb.png")
```

```{r}

df_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

## Try something else - leaflet

```{r}
df_airbnb |> 
  filter(price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  sample_n(500) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, radius = 0.5)
```


```{r}
df_airbnb |> 
  filter(price < 1000, 
    room_type == "Entire home/apt",
    borough == "Queens") |> 
  sample_n(500) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, radius = 0.5)
```

