---
title: "Case Study"
author: "Derek Lamb"
date: "`r Sys.Date()`"
output: html_document
---
```{r preferences}
library(tidyverse)
library(knitr)

opts_chunk$set(
  fig.width = 6,
  out.width = "90%"
)

## These are options that i'm going to treat as default for now
## I don't love viridis, but don't have a better option yet
theme_set(theme_bw() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Get data
```{r data}
library(p8105.datasets)
data(nyc_airbnb)

df_airbnb <- nyc_airbnb |> 
  rename(borough = neighbourhood_group) |> 
  mutate(stars = review_scores_location/2)
```

## Brainstorm questions
- Where are AirBNBs expensive?
  - Borough? Neighbourhood?
- How long are AirBNBs active?
  - Are AirBNBs illegal and do they get shut down?
- Which units have the most availability?  
- How is rating impacted by location? Price?
- How many apts are run by on host?
  - Does that affect price?
  - Does that vary by neighbrhood?
- Where are AirBNBs?
  - Borough? Neighborhood?
  -Lat and long?

